Differential Testing Runtime Engines--Lessons Learned from the JavaScript Domain

### 2018-07-11 paper/paper.tex
pass on IV.A

\subsection{Engines}
\label{sec:methodology:engines}~We selected the most popular JS
engines on the web~\Fix{ha alguma referencia que de suporte a isto?} to focus our bug-finding efforts, namely
Microsoft's Chakra~\cite{chakra2018repo}, Google's
v8~\cite{v82018repo}, Mozilla's
SpiderMonkey~\cite{spidermonkey2018repo}, and Apple's JavaScriptCore
(WebKit)~\cite{jsc2018repo}.

@@

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Test Suites
  % \Mar{try to use a single
  %     name (if possible) to facilitate reference in the paper. Use the
  % full path in the URL (citation) to indicate where one can find those
  % files.}
  }
  \begin{tabular}{ccr}
    \toprule
    TestSuite & Source & \# JS files \\
    \midrule
    Mozilla & \cite{mozilla} & 32,414 \\
    V8 & \cite{v8} & 64 \\
    WebKit & \cite{webkit} & 1,031 \\
    \midrule    
    Duktape & \cite{duktape} & 997 \\
    JerryScript & \cite{jerryscript} & 1,803 \\
    JSI & \cite{jsi} & 99 \\
    Tiny-js & \cite{tinyjs} & 44 \\    
    % Chakra & \cite{chakracore} & 2632 \\
    \midrule
     &  & 36,452 \\
   \bottomrule     
  \end{tabular}
\end{table}

>>>>

\subsection{Engines}
\label{sec:methodology:engines}~We selected 
JS engines according to the following criteria.

\begin{itemize}
\item Released latest version after Jan 1, 2018
\item Contains more than 1K starts, if on GitHub  
\item Uses a public issue tracker
\end{itemize}

The first criterion focuses on actively maintained projects whereas
the second criterion focuses on popular cases. As we wanted to report
bugs, we also looked for project with public issue trackers.
Table~\ref{tab:engines} shows the engines we selected in this
study. We made an exception to the second criterion with
XS~\Fix{cite}. As the project is young, \Fix{created in xx.yy.zz}), we
thought there was insufficient time to obtain 1K stars for XS. We
still considered this project as it seems to be attracting interest
from the community\Fix{is this true?}. It is worth noting that we used
JSVU~\cite{jsvu} to automatically install and configure versions of
different JS engines in our host environment. This is important as we
aim to use the most recent stable versions of each engine as to avoid
reporting old and already-fixed bugs to developers.

\begin{table}[t]
  \centering
  \caption{\label{tab:engines}Engines Analyzed}
  \begin{tabular}{ccr}
    \toprule
    Name & URL & \# Stars \\
    \midrule
    MS's Chakra & \cite{chakra2018repo} & - \\
    Google's v8 & \cite{v82018repo} & - \\
    Mozilla's SpiderMonkey & \cite{spidermonkey2018repo} & - \\
    Apple's JavaScriptCore (WebKit) & \cite{jsc2018repo} & - \\
   \bottomrule     
  \end{tabular}
\end{table}

@@

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Test Suites
  % \Mar{try to use a single
  %     name (if possible) to facilitate reference in the paper. Use the
  % full path in the URL (citation) to indicate where one can find those
  % files.}
  }
  \begin{tabular}{ccr}
    \toprule
    Name & Source & \# JS files \\
    \midrule
    Mozilla & \cite{mozilla} & 32,414 \\
    V8 & \cite{v8} & 64 \\
    WebKit & \cite{webkit} & 1,031 \\
    \midrule    
    Duktape & \cite{duktape} & 997 \\
    JerryScript & \cite{jerryscript} & 1,803 \\
    JSI & \cite{jsi} & 99 \\
    Tiny-js & \cite{tinyjs} & 44 \\    
    % Chakra & \cite{chakracore} & 2632 \\
    \midrule
     &  & 36,452 \\
   \bottomrule     
  \end{tabular}
\end{table}
